Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-03-23 paper.tex
Add 'vertical-axis' to title and start abstract

%=================================================================
\setcounter{page}{1}
\lastpage{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2014}
\history{Received: xx / Accepted: xx / Published: xx}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to
%arXiv.org
%\pdfoutput=1

@@

% Full title of the paper (Capitalized)
\Title{Effects of Reynolds Number on the Performance and Near-Wake of a
Cross-Flow Turbine}

@@

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{This is the abstract section. The abstract should be one section and
count less than 200 words. }

@@

\todo[inline]{Come up with a better title? Needs to be different from the METS
one, but not so blatantly the same.}

@@

\todo[inline]{Gotta get the JOT paper published first before we can say that!}

>>>>

%=================================================================
\setcounter{page}{1}
\lastpage{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2015}
\history{Received: xx / Accepted: xx / Published: xx}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to
%arXiv.org
%\pdfoutput=1

@@

% Full title of the paper (Capitalized)
\Title{Effects of Reynolds Number on the Performance and Near-Wake of a
Vertical-Axis Cross-Flow Turbine}

@@

% Abstract (Less than 200 words)
\abstract{The acceptable Reynolds number mismatch for scaled physical model
testing a cross-flow turbine is investigated experimentally.}

@@

@@
